Procrastination Tendencies of Company Corp. Customers

### 2017-12-02 MSDS_CaseStudy2_Master.Rmd
test commit

---
title: "MSDS Case Study 2 - Procrastination and HDI Data"
author: "Jose Torres and Lisa Street"
date: "November 29, 2017"  
output:
  html_document:
    keep_md: true
---

@@

## Load custom functions.

```{r custom functions}

@@

## Question 2: Read in and clean raw data

```{r Question2}

@@

## Question 3: HDI table scrape from Wikipedia

```{r Question3_HDI_table_scrape_from_Wikipedia}

@@

# Question 4: Preliminary Analysis

```{r Question4_Preliminary_Analysis, warning=FALSE}

@@

@@

#Create 4 plots for sample figure:

@@

## Question 5: Visualization and Deeper Analysis

```{r Question5_Preliminary_Analysis}

>>>>

---
title: "Procrastination Tendencies of Company Corp. Customers"
date: "November 29, 2017"
output:
  html_document:
    keep_md: true
authors: Jose Torres and Lisa Street
---

<br>

## Introduction

<br>

Procrastination is broadly defined as the avoidance of performing a task that needs to be accomplished.  The tasks in question can be of any magnitude and vary greatly in scope and impact.  A person's self view of their own procrastination tendencies can be difficult to measure or define. However, over the years several procrastination scales have been developed to help shed light on the subject. The impact of procrastination can be great, but the sooner a person can understand their own proclivity towards task avoidance, the better the chance they have to work on these challanges.

In order to gain better insight of the personal and work habits of it's customers, Company Corp. has asked the data scientists from Cool DS Inc to perform an analysis of the subject within it's own companies customer population. Since the customer count of Company Corp. is over 1 million, a random sample from the customer population of each country where Company Corp. retains a physical office, was taken. Each randomly assigned customer was given a survey that included questions regarding personal qualities such as age, income, marital status, etc., as well as a set of questions to be answered from four different procrastination scales. In addition, Cool DS Inc. aligned these results with the estimated Human Development Index factor for each country represented in the survey, to get a better idea of the correlation between a counties HDI and an individuals tendency to procrastinate. The following analysis details the findings from Cool DS Inc's study of procrastination within Company Corp.'s population.

<br>

@@

#### Load custom functions created by Cool DS Inc.

```{r custom_functions}

@@

```
<br>

#### Gather Data for Analysis

The first task performed by Cool DS Inc. was to survey 4,264 customers within Company Corp's universal customer population. The customers surveyed were taken by random sample and each customer was asked to fill out a questionaire of 61 variables.  Some of the variables were limited in answer by drop-down, and some allowed the customer to 'write-in' their own response.  Results of each individuals survey were tallied and consolidated into one master spreadhseet. Because write-in was allowed on some questions, data clean-up on the final consolidated survey was required.  The average procrastination score across the four procrastination scales was calculated as well. The information below details how the data transformation and cleanup was performed.

<br>

```{r, Question2}

@@

<br>

The Human Development Index (HDI) is a summary measure of average achievement in key dimensions of human development: a long and healthy life, being knowledgeable and have a decent standard of living. The HDI is the geometric mean of normalized indices for each of the three dimensions. _(ref: United Nation's Development Program)_
http://hdr.undp.org/en/content/human-development-index-hdi

In addition to the survey, data was scraped from the Wikipedia site noted below, which assigns the 2016 estimated HDI for 2015, by country. This data was then merged with they survey data, by country, in order to test for correlation between procrastination and the estimated HDI factor.

<br>

```{r, Question3_HDI_table_scrape_from_Wikipedia}

@@

<br>

#### Preliminary Analysis

Within the random population sample across Company Corp's offices, some of the respondents turned out to be minors. This was noted by any respondent with an age of 18 or under.  Company Corp. advised Cool DS Inc. that minors should not be included in the analysis, so these respondents were removed from further review. This resulted in a new subset of 4,036 respondents.

<br>

```{r, Question4_Preliminary_Analysis, warning=FALSE}

@@

<br>

One of the first things we can see from a statistical analysis across our data population, are the descriptive statistics on Age, Income, HDI and the average response for the four procrastionation scales.  Something to note is the N, or number of individuals measured in the descriptive statistic.  For annual income this number is 3,621.  This number is less than the 4,036 total population because some customers left this survey field empty.  Also to note, the N for HDI is 3,844.  This is due to some respondents not populating their county of residence within the survey. So when the HDI statistics were calculated, those with a country of residence of NA were not included.

<br>

```{r, Question4_Preliminary_Analysis2, warning=FALSE,echo=TRUE}

@@

<br>

The graphs below show a histogram of Age, HDI and Annual Income across respondents.  The boxplot chart gives shows a measure of the average of each of our procrastination scales.  THe histogram of Age shows as for the most part, normally distributed.  However, the HDI histogram shows as very left skewed and the histogram of Annual Income as fairly right skewed with a bit of bimodality.

Also included are frequency tables to give Company Corp. a better idea of the population distribution of it's customer base. What's interesting is the high number of individuals who self-describe as procrastinators and who are also viewed as procrastinators by others.

_Please note that the frequency tables for Occupation Category and Participants Per Country are rather large, so the top 10 and 20 of each table, respectively, are shown.  For details on how the Occupation Category keywords were matched, and for a list of the Remaining Counties in the Particpants per Country list, please see the 'Job_Keyword_Mapping.csv' and 'Remaing_Countries.csv' files for details._

<br>

```{r, Question4_Preliminary_Analysis3, warning=FALSE,echo=TRUE}

@@

<br>

#### Deeper Analysis and Visualization

A deeper analysis of the datas are also shown below. For several analyses, a mean value was taken to get a better perspective of the population as whole, instead of displaying unique values. This aides in the visualization of the variables. A few interesting things to note:

* There are 6 countries that exist in both DP and API top 15 Means.  They are:Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka   
  and Uraguay.

* As noted by the 'Average Annual Income vs Average Age' graph, there does seem to be a linear relationship between age and mean annual 	income until about age 40.  However, starting at around age 40, an income disparity between men and women can be seen that continues   with age.

* The 'Mean Life Satisfaction Mean by Mean HDI' scatterplot does not show a discernable relationship between the Satisfaction with Life
  Scale and mean HDI factor, however, the 'Mean Life Satisfaction per HDI Category' barplot below it does signify some relationship 
  between the Satisfaction with Life Scale and the HDI Category (Very High, High, Medium and Low), with the Low HDI Category having the   lowest SWLS average.

<br>

```{r, Question5_Preliminary_Analysis,echo=TRUE}
